The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018

### 2019-11-01 outputs/docs/paper/paper_MA_structure_edit.Rmd
topic results

Firstly, we describe the results of the CTM approach, which defined 80 topics over the period 1901 to 2018, and which we then further reduced to match the Comparative Agendas Project. We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.

## Topic modelling
We applied the CTM approach discussed in Appendix \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata). The main output of interest are the types of topics identified by the model, and the prevalence of each topic for each day of parliamentary discussion.

@@

Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Hansard. It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time. The highlighted topics are those related to war and conflict. The two chambers of the Australian Federal Parliament appear to be similar at a broad scale.

@@

Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history.

@@

The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term. The dashed lines show the elections. While the results here abstract from differences based on topic mix, the shape of the distribution seems to be reasonably similar. Given 80 topics, it may be difficult to see differences in the topic mix manually, and so we would like for the analysis model to be able to suggest whether the mix is changing. The second panel shows the 1983 election, and the subsequent change from Fraser to Hawke on 11 March 1983, identified by a dotted line on that date. The distribution of topics seems less bunched after the change, but it is difficult to tell how different it is. We would like the analysis model to be able to distinguish between the two if they seem different. The third panel shows the first Rudd term. The important aspect to note is that the period after the 2007 election and the Rudd term contain essentially the same Hansard dates. The analysis model needs to be able to deal with this situation.

Appendix \@ref(topicmodeleconresultsdiscussion) provides another example from the topic model results in the context of economic events.

>>>>

Firstly, we describe the results of the topic modeling and aggregation using the CTM approach, which defined 80 topics over the period 1901 to 2018,which we then further reduced to match the Comparative Agendas Project. We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.

## Topic modelling
We applied the CTM approach on the processed Hansard text database outlined in Section \@ref(hansarddata). The main output of interest are the types of topics identified by the model, and the prevalence of each topic for each day of parliamentary discussion.

@@

Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Hansard. The two panels refer to the two different chambers of the Australian Federal Parliament. The highlighted topics are categorised as 'Defense' in CAP terms, i.e. those related to war and conflict. The figure shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time; for example, the highlighted defense topics have notable peaks around the two World Wars, and post-9/11 attacks. The two chambers appear to be similar at a broad scale in terms of the increases and decreases in the different topics. Appendix \@ref(topicmodeleconresultsdiscussion) provides another example from the topic model results in the context of economic events.

@@

Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history. 
The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term. The dashed lines show the elections. While the results here abstract from differences based on topic mix, the shape of the distribution seems to be reasonably similar. Given 80 topics, it may be difficult to see differences in the topic mix manually, and so we would like for the analysis model to be able to suggest whether the mix is changing. The second panel shows the 1983 election, and the subsequent change from Fraser to Hawke on 11 March 1983, identified by a dotted line on that date. The distribution of topics seems less bunched after the change, but it is difficult to tell how different it is. We would like the analysis model to be able to distinguish between the two if they seem different. The third panel shows the first Rudd term. The important aspect to note is that the period after the 2007 election and the Rudd term contain essentially the same Hansard dates. The analysis model needs to be able to deal with this situation. XX I FIND THESE FIGURES HARD TO READ... CONSIDER REDOING OR REMOVING XX

@@
